\bf Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-07-23 manuscript/main.tex
delete gram matrix testthat
man: wrote down the penalized least square criterion

	\subsection{Preliminary step: Finite-basis Approximation }\label{sec: finite basis approximation}	
	Let ${b_m(t)}$ be a twice-differentiable basis of $L^2([0,1])$ whose second derivatives are also linearly independent, for example, cubic B-splines, the Fourier basis, or an orthonormal polynomial basis of degree greater than three. Using this basis, the $j$th functional predictor, regression coefficient, and PLS direction (suppressing iteration indices) are represented as follows:
	\begin{equation*}
		X_{ij}(t) = \sum_{m=1}^\infty \theta_{ijm} \, b_m(t),\quad
		\beta_j(t) = \sum_{m=1}^\infty \eta_{jm} \, b_m(t),\quad
		%%%%%%%%%%%%%%%%%%%%%%
		\xi_j(t)
		=
		\sum_{m=1}^\infty
		\gamma_{jm}
		b_m(t)
	\end{equation*}	
	In practice, the full set of coefficients can not be obtained  with finite sample size, as functional data are measured on a finite grid. Thus, we truncate the expansion at $M$ terms and define the truncated basis space
	$
	\mathcal{B} := \operatorname{span}\bigl(b_1(t), \ldots, b_M(t)\bigr).
	$
	We choose a moderately large $M$ (e.g., 15 or 20) to capture functional variation without fine-tuning, as smoothness is handled via penalization (see Section~\ref{sec: Regularization of PLS Components}).
	The truncated expansions of the predictor and coefficient are denoted as
	\begin{equation*}
		\widetilde{X}_{ij}(t) := \sum_{m=1}^M \theta_{ijm} \, b_m(t), \quad
		\tilde{\beta}_j(t) := \sum_{m=1}^M \eta_{jm} \, b_m(t),
	\end{equation*}
	and our suggest method restricts each PLS direction to admit the following expansion:
	\begin{equation*}
		\xi_j(t) = \sum_{m=1}^M \gamma_{jm} \, b_m(t).
	\end{equation*}
	This implies that all computations in this paper are carried out entirely within the subspace
	\begin{equation}\label{def:truncated_hilbert_space}
		\widetilde{ \mathcal{H} } := \mathcal{B}^K \times \mathbb{R}^p \subset \mathcal{H}.
	\end{equation}
	The $i$th hybrid predictor, projected on $\widetilde{ \mathcal{H} }$, is represented by the tuple
	\begin{equation*}
		\widetilde{W}_i := 
		(
		\widetilde{X}_{i1}, \ldots, \widetilde{X}_{iK}, \boldsymbol{Z}_i
		).
	\end{equation*}
	Let $\boldsymbol{\theta}_{ij}$, $\boldsymbol{\eta}_j$, and $\boldsymbol{\gamma}_j$ denote the $M$-dimensional vectors of coefficients:
	\begin{equation}\label{def:coef_vector_form}
		\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top,
		\quad
		\boldsymbol{\eta}_{j} := (\eta_{j1}, \ldots, \eta_{jM})^\top ,
		\boldsymbol{\gamma}_{j} := (\gamma_{j1}, \ldots, \gamma_{jM})^\top.
	\end{equation}
	For the predictors, we stack the coefficient vectors across observations into the matrix
	\begin{equation}
		\Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M}.
	\end{equation}
	The full data for the hybrid PLS problem can be represented by the tuple
	\begin{equation}\label{def:problem_instance}
		(\mathbb{B}, \mathbb{B}^{\prime\prime}, \Theta, \mathbf{y}) \in 
		\mathbb{R}^{(MK+p) \times (MK+p)} \times 
		\mathbb{R}^{(MK+p) \times (MK+p)} \times 
		\mathbb{R}^{n \times (MK+p)} \times 
		\mathbb{R}^n,
	\end{equation}
	where $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ are the Gram matrices of the basis functions and their second derivatives, with entries
	\begin{equation}
		B_{m, m'} := \int_0^1 b_m(t)\, b_{m'}(t)\, dt, \quad
		B^{\prime\prime}_{m, m'} := \int_0^1 b_m''(t)\, b_{m'}''(t)\, dt,
	\end{equation}
	for $m, m' = 1, \ldots, M$. We then define the block-diagonal matrices
	\begin{equation}\label{def:gram_block}
		\mathbb{B} := \operatorname{blkdiag}(B, \ldots, B, I_p), \quad
		\mathbb{B}^{\prime\prime} := \operatorname{blkdiag}(B^{\prime\prime}, \ldots, B^{\prime\prime}, I_p),
	\end{equation}
	the full design matrix $\Theta := (\Theta_1, \ldots, \Theta_K, Z) \in \mathbb{R}^{n \times (MK + p)}$, and the response vector $\mathbf{y} := (y_1, \ldots, y_n)^\top$.

@@

	We describe the strategy at the $l$-th iteration. For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for details). The  PLS component direction is estimated by the unit-norm direction $\xi \in \widetilde{\mathcal{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$, defined as

@@

	\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
	Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions. To address this, we propose a regularized extension that balances predictive performance with smoothness. Specifically, we penalize the roughness of each $\hat{\xi}_j$ using its integrated squared second derivative 
	\begin{equation}
		\operatorname{PEN}(\hat{\xi}_j) := \int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt.
	\end{equation}

@@

	\medskip
	\noindent{\textit{Computation.}}~The generalized eigenproblem presented in Proposition~\ref{proposition:eigen_regul}  may be computationally unstable in practice. However, by leveraging the rank-one structure of the matrix 
	$V$
	Proposition \ref{proposition:linear_regul} derives a closed-form solution that requires only the solution of linear systems.
	\begin{proposition}[Closed-form solution]  
		\label{proposition:linear_regul}  
		Consider the optimization problem described in Proposition~\ref{proposition:eigen_regul}. Define the following quantities, which depend on the observed data but are not decision variables:  
		\[
		\mathbf{u}_j := B \Theta_j^\top \mathbf{y} \in \mathbb{R}^M \quad \text{for } j = 1, \ldots, K, \quad \text{and} \quad \mathbf{v} := Z^\top \mathbf{y} \in \mathbb{R}^p.
		\]  
		Let
		\[
		q := \sum_{j=1}^K \mathbf{u}_j^\top (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j + \mathbf{v}^\top \mathbf{v}.
		\]

@@

	\subsection{Step 2: Computing Residualized Predictors via Hybrid-on-Scalar Regression} \label{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}
	The second step of the PLS algorithm involves iteratively obtaining the ($l+1$)-th residualized predictors as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$, where $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ is the least squares estimate from regressing the previous ($l$-th) residualized outcome $\mathbf{W}_i^{[l]}[\mathbf{t}]$ on the corresponding  estimated PLS score $\widehat{\rho}_{il}$.  The pointwise least squares estimate, $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] = (\sum_{i=1}^n \mathbf{W}_i^{[l]}[\mathbf{t}] \widehat{\rho}_{il})/(\sum_{i=1}^n \widehat{\rho}_{il}^2)$, presented in Section \ref{sec: Naive PLS Algorithm}, however, is  highly inefficient and may not be even feasible for multiple dense and/or irregular functional data. Moreover, the pointwise least squares estimator can show substantial variability across the domain, which becomes problematic for the entire algorithm as its instability passes on to subsequent residualized outcomes and PLS components. Therefore, in this section, we introduce a novel strategy based on a hybrid-on-scalar regression model for obtaining $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ and implementing the second step.

	Again, we omit $l$ in the notations. Let $\widehat{\boldsymbol{\rho}}=(\widehat{\rho}_1, \ldots, \widehat{\rho}_n)^\top$ denote an $n$-dimensional vector of PLS scores estimated from the proposed algorithm, and let the $(K+P)$-vector $\boldsymbol{\delta}[\mathbf{t}] = [\pi(\mathbf{t})^\top, \boldsymbol{\gamma}^\top]^\top$ denote the regression coefficient consisting of the functional part $\pi(\mathbf{t}) = (\pi^{(1)}(t_1), \ldots,\pi^{(K)}(t_K))^\top \in \mathbb{R}^K$ and scalar part $\boldsymbol{\gamma} = (\gamma_1, \ldots,\gamma_p)^\top \in \mathbb{R}^p$. The hybrid-on-scalar regression model we are interested in fitting is then:
	\begin{equation}
		\widetilde{W}[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top + \mathbf{e}[\mathbf{t}],
		\label{eq: hybrid on scalar regression model}
	\end{equation}
	where $\mathbf{e}[\mathbf{t}]$ is an $n \times (K+p)$ matrix of errors.

	As in Section \ref{subsec: Step 1: Computing Smoothed PLS components}, the hybrid response can be expanded using basis functions as $\widetilde{W}[\mathbf{t}] = \widetilde{C}^* B^*[\mathbf{t}]$. Similarly, we expand each functional regression coefficient using the basis functions as $\pi^{(k)}(t_k) =\sum_{m=1}^M d_m^{(k)} b^{(k)}_m(t_k) = \boldsymbol{\gamma}^{(k)\top} \mathbf{b}^{(k)}(t_k)$, where $\boldsymbol{\gamma}^{(k)} = (d_1^{(k)}, \ldots, d_M^{(k)})\top \in \mathbb{R}^M$ are basis coefficients. Here, a different basis system can be flexibly chosen to expand the regression coefficient, but without loss of generality we use the same system as in Section \ref{subsec: Step 1: Computing Smoothed PLS components}. With the $(MK+p)$-dimensional row vector $\boldsymbol{\gamma}^* = (\boldsymbol{\gamma}^{(1)\top}, \ldots, \boldsymbol{\gamma}^{(K)\top}, \gamma_1, \ldots, \gamma_p)$ that stacks the basis coefficients and scalar regression coefficients, we can express the linear predictor of the regression as: $\widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}]$. Finally, these basis expansions of the hybrid response and the regression coefficient enable us to re-write the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model} in a finite-dimensional form:
	\begin{equation}
		\widetilde{C}^* B^*[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}] + \mathbf{e}[\mathbf{t}].
		\label{eq: rewritten hybrid on scalar regression model}
	\end{equation}

@@

	The step for obtaining the subsequent residualized response is identical to that of the naive PLS algorithm in  in Section \ref{sec: Naive PLS Algorithm}. Specifically, the $(l-1)$-th residualized response can be obtained as $Y_i^{[l+1]} = Y_i^{[l]} - \widehat{\nu}_l \widehat{\rho}_{il}$, where $\widehat{\nu}_l = \sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{il}/\sum_{i=1}^n \widehat{\rho}_{il}^2$  is the least square estimate of the simple linear model regressing $Y_i^{[l]}$ on $\widehat{\rho}_{il}$.

>>>>

	\subsection{Preliminary step: Finite-basis Approximation }\label{sec: finite basis approximation}	
	Let ${b_m(t)}$ be a twice-differentiable basis of $L^2([0,1])$ whose second derivatives are also linearly independent, for example, cubic B-splines, the Fourier basis, or an orthonormal polynomial basis of degree greater than three. Using this basis, the $j$th functional predictor, regression coefficient,  PLS direction (suppressing iteration indices) are represented as follows:
	\begin{equation*}
		X_{ij}(t) = \sum_{m=1}^\infty \theta_{ijm} \, b_m(t),\quad
		\beta_j(t) = \sum_{m=1}^\infty \eta_{jm} \, b_m(t),\quad
		%%%%%%%%%%%%%%%%%%%%%%
		\xi_j(t)
		=
		\sum_{m=1}^\infty
		\gamma_{jm}
		b_m(t)
	\end{equation*}	
	In practice, the full set of coefficients can not be obtained  with finite sample size, as functional data are measured on a finite grid. Thus, we truncate the expansion at $M$ terms and define the truncated basis space
	$
	\mathcal{B} := \operatorname{span}\bigl(b_1(t), \ldots, b_M(t)\bigr).
	$
	We choose a moderately large $M$ (e.g., 15 or 20) to capture functional variation without fine-tuning, as smoothness is handled via penalization (see Section~\ref{sec: Regularization of PLS Components}).
	The truncated expansions of the predictor and coefficient are denoted as
	\begin{equation*}
		\widetilde{X}_{ij}(t) := \sum_{m=1}^M \theta_{ijm} \, b_m(t), \quad
		\tilde{\beta}_j(t) := \sum_{m=1}^M \eta_{jm} \, b_m(t),
	\end{equation*}
	and our suggest method restricts each PLS direction to admit the following expansion:
	\begin{equation*}
		\xi_j(t) = \sum_{m=1}^M \gamma_{jm} \, b_m(t).
	\end{equation*}
	This implies that all computations in this paper are carried out entirely within the subspace
	\begin{equation}\label{def:truncated_hilbert_space}
		\widetilde{ \mathcal{H} } := \mathcal{B}^K \times \mathbb{R}^p \subset \mathcal{H}.
	\end{equation}
	The $i$th hybrid predictor, projected on $\widetilde{ \mathcal{H} }$, is represented by the tuple
	\begin{equation*}
		\widetilde{W}_i := 
		(
		\widetilde{X}_{i1}, \ldots, \widetilde{X}_{iK}, \boldsymbol{Z}_i
		).
	\end{equation*}
	Let $\boldsymbol{\theta}_{ij}$, $\boldsymbol{\eta}_j$, and $\boldsymbol{\gamma}_j$ denote the $M$-dimensional vectors of coefficients:
	\begin{equation}\label{def:coef_vector_form}
		\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top,
		\quad
		\boldsymbol{\eta}_{j} := (\eta_{j1}, \ldots, \eta_{jM})^\top ,
		\boldsymbol{\gamma}_{j} := (\gamma_{j1}, \ldots, \gamma_{jM})^\top.
	\end{equation}
	For the predictors, we stack the coefficient vectors across observations into the matrix
	\begin{equation}
		\Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M}.
	\end{equation}
	The full data for the hybrid PLS problem can be represented by the tuple
	\begin{equation}\label{def:problem_instance}
		(\mathbb{B}, \mathbb{B}^{\prime\prime}, \Theta, \mathbf{y}) \in 
		\mathbb{R}^{(MK+p) \times (MK+p)} \times 
		\mathbb{R}^{(MK+p) \times (MK+p)} \times 
		\mathbb{R}^{n \times (MK+p)} \times 
		\mathbb{R}^n,
	\end{equation}
	where $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ are the Gram matrices of the basis functions and their second derivatives, with entries
	\begin{equation}
		B_{m, m'} := \int_0^1 b_m(t)\, b_{m'}(t)\, dt, \quad
		B^{\prime\prime}_{m, m'} := \int_0^1 b_m''(t)\, b_{m'}''(t)\, dt,
	\end{equation}
	for $m, m' = 1, \ldots, M$. We then define the block-diagonal matrices
	\begin{equation}\label{def:gram_block}
		\mathbb{B} := \operatorname{blkdiag}(B, \ldots, B, I_p), \quad
		\mathbb{B}^{\prime\prime} := \operatorname{blkdiag}(B^{\prime\prime}, \ldots, B^{\prime\prime}, I_p),
	\end{equation}
	the full design matrix $\Theta := (\Theta_1, \ldots, \Theta_K, Z) \in \mathbb{R}^{n \times (MK + p)}$, and the response vector $\mathbf{y} := (y_1, \ldots, y_n)^\top$.

@@

	We describe the strategy at the $l$-th iteration. %For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for details). 
	The  PLS component direction is estimated by the unit-norm direction $\xi^{[l]} \in \widetilde{\mathcal{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$, defined as

@@

	\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
	Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions. To address this, we propose a regularized extension that balances predictive performance with smoothness. Specifically, we penalize the roughness of each $\hat{\xi}_j$ using its integrated squared second derivative 
	\begin{equation}\label{def:roughness_penalty}
		\operatorname{PEN}(\hat{\xi}_j) := \int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
		.
	\end{equation}

@@

	\medskip
	\noindent{\textit{Computation.}}~The generalized eigenproblem presented in Proposition~\ref{proposition:eigen_regul}  may be computationally unstable in practice. However, by leveraging the rank-one structure of the matrix 
	$V$
	Proposition \ref{proposition:linear_regul} derives a closed-form solution that requires only the solution of linear systems.
	\begin{proposition}[Closed-form solution]  
		\label{proposition:linear_regul}  
		Consider the optimization problem described in Proposition~\ref{proposition:eigen_regul}. Define the following quantities, which depend on the observed data but are not decision variables:  
		\[
		\mathbf{u}_j := B \Theta_j^\top \mathbf{y} \in \mathbb{R}^M \quad \text{for } j = 1, \ldots, K, \quad \text{and} \quad \mathbf{v} := \mathbf{Z}^\top \mathbf{y} \in \mathbb{R}^p.
		\]  
		Let
		\[
		q := \sum_{j=1}^K \mathbf{u}_j^\top (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j + \mathbf{v}^\top \mathbf{v}.
		\]

@@

	\subsection{Step 2: Computing Residualized Predictors via Hybrid-on-Scalar Regression} \label{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}
The $l$-th iteration's second step involves orthogonalization. This is achieved by fitting a hybrid-on-scalar regression model, $$\widetilde{W}^{[l]}_i = \hat{\rho}^{[l]}\, \delta^{[l]} + E_i^{[l]},$$ and then taking the residuals. Here, $\delta^{[l]}$ and $E_i^{[l]}$ are the regression coefficient and error terms, respectively, both elements of $\tilde{\mathcal{H}}$ defined in \eqref{def:truncated_hilbert_space}. In the same spirit as in Section \ref{sec: Regularization of PLS Components}, we want the estimated regression coefficieint $\hat{\delta}^{[l]} 
= 
(\hat{\delta}^{[l]}_1, \ldots, \hat{\delta}^{[l]}_K, \hat{\boldsymbol{\chi}}^{[l]} )$ 
have  smooth functional parts, for the whole PLS estimation proecedure to be stable.
Therefore, we obtain $\delta^{[l]}$ by minimizing the followign penaluized least square criteria, where the functional part is penalized by 
 integeraed squared second derivative defined in \eqref{def:roughness_penalty}:
 \begin{align*}
\operatorname{PENSSE}( \delta)
&=
\sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta,
\,
\widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta
\rangle_{\mathcal{H}}
%%%%%%%%%%%%%%%%%%%%
\\&=
\sum_{i=1}^n 
\langle \widetilde{W}_i^{[l]},  \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}
+
\sum_{i=1}^n 
\langle \delta,  \, \delta \rangle_{\mathcal{H}}
-
\sum_{i=1}^n 
( \hat{\rho}_i^{[l]} )^2
\langle \delta,  \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}
 \end{align*}

%As in Section \ref{subsec: Step 1: Computing Smoothed PLS components}, the hybrid response can be expanded using basis functions as $\widetilde{W}[\mathbf{t}] = \widetilde{C}^* B^*[\mathbf{t}]$. Similarly, we expand each functional regression coefficient using the basis functions as $\pi^{(k)}(t_k) =\sum_{m=1}^M d_m^{(k)} b^{(k)}_m(t_k) = \boldsymbol{\gamma}^{(k)\top} \mathbf{b}^{(k)}(t_k)$, where $\boldsymbol{\gamma}^{(k)} = (d_1^{(k)}, \ldots, d_M^{(k)})\top \in \mathbb{R}^M$ are basis coefficients. Here, a different basis system can be flexibly chosen to expand the regression coefficient, but without loss of generality we use the same system as in Section \ref{subsec: Step 1: Computing Smoothed PLS components}. With the $(MK+p)$-dimensional row vector $\boldsymbol{\gamma}^* = (\boldsymbol{\gamma}^{(1)\top}, \ldots, \boldsymbol{\gamma}^{(K)\top}, \gamma_1, \ldots, \gamma_p)$ that stacks the basis coefficients and scalar regression coefficients, we can express the linear predictor of the regression as: 
$\widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}]$. Finally, these basis expansions of the hybrid response and the regression coefficient enable us to re-write the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model} in a finite-dimensional form:
\begin{equation}
	\widetilde{C}^* B^*[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}] + \mathbf{e}[\mathbf{t}].
	\label{eq: rewritten hybrid on scalar regression model}
\end{equation}
$\mathbf{e}[\mathbf{t}]$ is an $n \times (K+p)$ matrix of errors. 
\\

@@

	The step for obtaining the subsequent residualized response is identical to that of the naive PLS algorithm in  in Section \ref{sec: Naive PLS Algorithm}. Specifically, the $(l-1)$-th residualized response can be obtained as $Y_i^{[l+1]} = Y_i^{[l]} - \widehat{\nu}_l \widehat{\rho}_{il}$, where $\widehat{\nu}_l = \sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{il}/\sum_{i=1}^n \widehat{\rho}_{il}^2$  is the least square estimate of the simple linear model regressing $Y_i^{[l]}$ on $\widehat{\rho}_{il}$.
	 the PLS algorithm involves iteratively obtaining the ($l+1$)-th residualized predictors as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$, where $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ is the least squares estimate from regressing the previous ($l$-th) residualized outcome $\mathbf{W}_i^{[l]}[\mathbf{t}]$ on the corresponding  estimated PLS score $\widehat{\rho}_{il}$.  The pointwise least squares estimate, $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] = (\sum_{i=1}^n \mathbf{W}_i^{[l]}[\mathbf{t}] \widehat{\rho}_{il})/(\sum_{i=1}^n \widehat{\rho}_{il}^2)$, presented in Section \ref{sec: Naive PLS Algorithm}, however, is  highly inefficient and may not be even feasible for multiple dense and/or irregular functional data. Moreover, the pointwise least squares estimator can show substantial variability across the domain, which becomes problematic for the entire algorithm as its instability passes on to subsequent residualized outcomes and PLS components. Therefore, in this section, we introduce a novel strategy based on a hybrid-on-scalar regression model for obtaining $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ and implementing the second step.

	Again, we omit $l$ in the notations. Let $\widehat{\boldsymbol{\rho}}=(\widehat{\rho}_1, \ldots, \widehat{\rho}_n)^\top$ denote an $n$-dimensional vector of PLS scores estimated from the proposed algorithm, and let the $(K+P)$-vector $\boldsymbol{\delta}[\mathbf{t}] = [\pi(\mathbf{t})^\top, \boldsymbol{\gamma}^\top]^\top$ denote the regression coefficient consisting of the functional part $\pi(\mathbf{t}) = (\pi^{(1)}(t_1), \ldots,\pi^{(K)}(t_K))^\top \in \mathbb{R}^K$ and scalar part $\boldsymbol{\gamma} = (\gamma_1, \ldots,\gamma_p)^\top \in \mathbb{R}^p$.
